Open Preprints in Ecology \& Evolution

### 2012-09-22 ms.tex
minor modif
merge

The review process as a whole is critically over-loaded, because the
number of active scientists increases, because the pressure to publish
increases, and because of an effect dubbed ``the tragedy of the
reviewers commons'' REF.  At the same time, rejection rates are high
in most journals (REF), and when not invited to submit revisions,
authors are left with the impression that they must start the whole
process all over again. It's thus no surprise that different
initiatives emerged over the last few years to decrease the time spent
in review. XXX et coll. (REF) called for the recycling and reuse of
peer-reviews: by attaching previous reviews, and detailed replies, to
a new submission, both the editor and the referees can gauge the work
done on the manuscript, and perhaps evaluate it with less
prejudice. In a similar way, the \emph{Peerage of Science} initiative
allows authors to seek anonymous pre- review by their peers. Some
journals (LIST?) now accept papers for publication that received good
evaluations, effectively outsourcing the review process. A widespread
use of preprint servers can achieve the same goal of reducing the time
spent in review. By putting a manuscript out there for open comments
and criticisms, the authors will receive valuable feedback, and can
improve the version which will be submitted. With a rich enough
community of scientists depositing preprints, and commenting on them,
the process of an open pre- review can become widespread, and will
overall increase the quality of first submissions.
% Assuming that the quality of the paper is a good prior of its acceptance probability :-)

>>>>

% Tim's section:
The review process as a whole is critically over-loaded, because the number of
active scientists increases, because the pressure to publish increases, and
because of an effect dubbed ``the tragedy of the reviewers commons'' REF.  In
the same times, rejection rates are high in most journals (REF), and when the
not invited to submit a revisions, authors are left with the impression that
they must start the whole process all over again. It's thus no surprise that
different initiatives emerged over the last few years, to decrease the time
spent in review. XXX et coll. (REF) called for the recycling and reuse of
peer-reviews: by attaching previous reviews, and detailed replies, to a new
submission, both the editor and the referees can gauge the work done on the
manuscript, and perhaps evaluate it with less prejudice. In a similar way, the
\emph{Peerage of Science} initiative allows authors to seek anonymous pre-
review by their peers. Some journals (LIST?) now accept to publish papers
which received good evaluations, effectively outsourcing the review process. A
widespread use of preprint servers can achieve the same goal of reducing the
time spent in review. By putting a manuscript out there for open comments and
criticisms, the authors will receive valuable feedback, and can improve the
version which will be submitted. With a rich enough community of scientists
depositing preprints, and commenting on them, the process of an open pre-
review can become widespread, and will overall increase the quality of first
submissions.
